---
title: "2018-10-31"
author: "410773012"
date: "10/31/2018"
output: html_document
---

```{r}
library(googlesheets)
gs_auth(new_user = TRUE)
gsSurvey<-gs_key("1mC9bnxj11NCNoOCw0Vmn4nxERbHtLjeGo9v9C9b2GDE")  #download sheet information as an object
classSurvey<-gs_read(gsSurvey,ws=1) #access the 1st worksheet
```

```{r}
library(stringr)
aa<-(str_sub(classSurvey$居住地行政區,1,3))
classSurvey[aa == "台北市",c("姓名")]
```

```{r}
cc<-classSurvey[aa == "台北市",c("姓名")]
class(cc)
cc$姓名[3]
```

```{r}
bb<-c("a","b","c")
bb[2]
```

```{r}
StuDF <- data.frame(
  StuID=c(1,2,3,4,5),
  name=c("小明","大雄","胖虎","小新","大白"),
  score=c(80,60,90,70,50)
  )
StuDF 
```

```{r}
names(gsSurvey)
```

```{r}
gsSurvey$links$type
```

```{r}
names(StuDF)[2] <- c("姓名")
names(StuDF)
```

```{r}
names(StuDF) <- c("學號","姓名","成績")
names(StuDF)
```

```{r}
library(readr)
student <- read_csv("https://raw.githubusercontent.com/tpemartin/course-107-1-programming-for-data-science/master/data/student.csv")
library(dplyr)
library(magrittr)
student %<>% mutate(
  身高級距=cut(身高,c(0,150,155,160,165,170,175,180,185,200)))
```
```{r}
levels(student$身高級距)
```
```{r}
library(readr)
student <- read_csv("https://raw.githubusercontent.com/tpemartin/course-107-1-programming-for-data-science/master/data/student.csv")
library(dplyr)
library(magrittr)
student %<>% mutate(
  身高級距=cut(身高,c(0,150,155,160,165,170,175,180,185,200)))
```
```{r}
levels(student$身高級距)
```
```{r}
StuDF$成績[c(4)]
StuDF$成績[c(4)] <- 75
```
```{r}

```






library(stringr)
x <-str_replace(iPeenData$均消, ",","")
z <-str_extract_all(x,"[0-9]+")
as.integer(z)
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

